---
title: "Lab 4--MATH 243"
author: "Theodore Dounias"
date: "October 3, 2017"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
war <- read.csv("http://www.stat.cmu.edu/~cshalizi/uADA/15/hw/06/ch.csv", row.names = 1)
library(tidyverse)
library(glmnet)
attach(war)
```

**1**
     
```{r}
war <- war %>%
  mutate(exports_quad = exports^2)

cw_logit <- glm(start ~ exports + schooling + growth + peace + concentration + lnpop + fractionalization + dominance + exports_quad, family = binomial, data = war)

summary(cw_logit)
```
    
All predictors apart from dominance are statistically significant at the 5% level.
   
**2**
   
```{r}
#1

ind_1975 <- war %>%
  filter(country == "India", year == "1975") %>%
  select(-(1:3))

predict(cw_logit, type = "response", ind_1975)

ind_1975[2] <- ind_1975[2] + 30

predict(cw_logit, type = "response", ind_1975)

ind_1975 <- war %>%
  filter(country == "India", year == "1975") %>%
  select(-(1:3))

ind_1975[1] <- ind_1975[1] + 0.1

predict(cw_logit, type = "response", ind_1975)

#2

nig_1965 <- war %>%
  filter(country == "Nigeria", year == "1965") %>%
  select(-(1:3))

predict(cw_logit, type = "response", nig_1965)

nig_1965[2] <- nig_1965[2] + 30

predict(cw_logit, type = "response", nig_1965)

nig_1965 <- war %>%
  filter(country == "Nigeria", year == "1965") %>%
  select(-(1:3))

nig_1965[1] <- nig_1965[1] + 0.1

predict(cw_logit, type = "response", nig_1965)
```
    
The difference in probabilities is not the same because we are dealing with log odds, not with a linear association. Therefore a change in a variable will not have the same effect ranging between two different observations. The function for getting a probability here is dependant on both the relative difference--here what we add to the observed values--and the prior state of the values of the observations.
    
**3**
    
```{r}
#1
my_log_pred <- ifelse(cw_logit$fit < 0.5, "No", "Yes")
Civ_war <- mutate(na.omit(war), civ_war_Yes = ifelse(start == 1, "Yes", "No"))

conf_log <- table(my_log_pred, Civ_war$civ_war_Yes)
conf_log

#2
(1/nrow(Civ_war)) * (conf_log[2, 1] + conf_log[1, 2])


#3
count <- war %>%
  filter(!is.na(start)) %>%
  summarize(n_start = sum(start))

(1/sum(!is.na(start)))*count[1, 1]

(1/nrow(Civ_war))*sum(Civ_war$civ_war_Yes == "Yes")
```

```{r}

```


    
```{r}

```

