---
title: "Lab 7 -- MATH 243"
author: "Theodore Dounias"
date: "11/21/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
poverty <- read.delim("https://raw.githubusercontent.com/andrewpbray/math-243/master/assets/data/poverty.txt", header = TRUE)
library(ggplot2)
library(voteogram)
library(tidyverse)
```

####Part I
   
**1**
```{r}
set.seed(40)

km2 <- kmeans(poverty[ ,-1], 2, nstart = 20)

km3 <- kmeans(poverty[ ,-1], 3, nstart = 20)

km4 <- kmeans(poverty[ ,-1], 4, nstart = 20)
```

**2-3**
```{r}
pca <- prcomp(poverty[, -1])

d <- data.frame(PC1 = pca$x[, 1],
                PC2 = pca$x[, 2],
                cluster2 = as.factor(km2$cluster),
                cluster3 = as.factor(km3$cluster),
                cluster4 = as.factor(km4$cluster),
                state = poverty$State)

ggplot(d, aes(x = PC1, y = PC2, col = cluster2)) +
  geom_point() +
  geom_text(aes(label = state), hjust = 0, vjust = 0, size = 3)

ggplot(d, aes(x = PC1, y = PC2, col = cluster3)) +
  geom_point() +
  geom_text(aes(label = state), hjust = 0, vjust = 0, size = 3)

ggplot(d, aes(x = PC1, y = PC2, col = cluster4)) +
  geom_point() +
  geom_text(aes(label = state), hjust = 0, vjust = 0, size = 3)
```
   
**4**
```{r}
km1 <- kmeans(poverty[ ,-1], 1, nstart = 20)

km5 <- kmeans(poverty[ ,-1], 5, nstart = 20)

df <- data.frame("K" = 1:5,
                 "SS" = c(km1$tot.withinss,
                          km2$tot.withinss,
                          km3$tot.withinss,
                          km4$tot.withinss,
                          km5$tot.withinss
                          ))
ggplot(df, aes(x = K, y = SS)) +
  geom_point() +
  geom_line()
```
   
####Part II
   
**1**   
```{r}
j_act <- roll_call(critter = "house", 115, session = "1", 637)

#Name
j_act

#Date
j_act$date_of_vote

#Did it pass?
j_act$result

#Margin
j_act$total_yes - (j_act$total_no + j_act$total_not_voting)

#Oregon reps?
ore_rep <- j_act$votes %>%
  filter(state_abbrev == "OR")

ore_rep

#Cartogram
house_carto(j_act, pp_square=TRUE) +
  labs(x=NULL, y=NULL, 
       title="House Vote - Tax Cuts and Jobs Act") 
```
   
**2**
```{r}
votes <- matrix(NA, nrow = 435, ncol = 50)
rcall_ind <- 588:637

for(i in 1:length(rcall_ind)) {
  print(rcall_ind[i])
  votes[, i] <- roll_call("house", 115, 1, rcall_ind[i])$votes$position
}

vote_yes <- votes == "Yes"

party <- roll_call("house", 115, 1, 637)$votes$party
```
  
Each row is a different vote. Each column represents a different house representative. Vote_yes is a matrix of logical values (1/0) while votes is a matrix of characters that happen to be "Yes" and "No".
     
**3**
```{r}
vote_k2 <- kmeans(vote_yes, 2, nstart = 20)

pty_kmeans <- vote_k2$cluster == "1"

pty_real <- party == "R"

1 - sum(pty_kmeans[-435] + pty_real[-435] != 1)/434
```
  
Therefore the missclassification on party is a little more than a third. We would say that k-means clusters does not produce a good division down party lines.
   
**4**
```{r}
vote_k1 <- kmeans(vote_yes, 1, nstart = 20)

vote_k3 <- kmeans(vote_yes, 3, nstart = 20)

vote_k4 <- kmeans(vote_yes, 4, nstart = 20)

vote_k5 <- kmeans(vote_yes, 5, nstart = 20)

vote_k6 <- kmeans(vote_yes, 6, nstart = 20)

df <- data.frame("K" = 1:6,
                 "SS" = c(vote_k1$tot.withinss,
                          vote_k2$tot.withinss,
                          vote_k3$tot.withinss,
                          vote_k4$tot.withinss,
                          vote_k5$tot.withinss,
                          vote_k6$tot.withinss
                          ))
ggplot(df, aes(x = K, y = SS)) +
  geom_point() +
  geom_line()
```
   
This plot tells us that there is very significant clustering along two clusters in the voting patterns in these bills. After 4 clusters there is almost no variance left to explain.
    
```{r}
pca <- prcomp(vote_yes)

d <- data.frame(PC1 = pca$x[, 1],
                PC2 = pca$x[, 2],
                cluster4 = as.factor(vote_k4$cluster),
                party)

ggplot(d, aes(x = PC1, y = PC2, col = cluster4)) +
  geom_point() +
  geom_text(aes(label = party), hjust = 0, vjust = 0, size = 3)

```
  
**6**
   
The first several principle components serve to inform us of latent meta-variables present in our dataset. For example here, as mentioned in class, it is not strictly party lines that are dictating the way a representative votes, but affinity to small or big government practices. This could not have been infered without examining the principle components more closely. 
